---
title: "Test Questions Practice exam"
author: "Michiel Noback"
date: "9/17/2019"
output:
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the data

You are going to analyse a dataset that describes some properties of a variety of food constituents. In the column header, `carb` stands for carbohydrate, `fat.sat` for saturated fats, and `fat.unsat` for unsaturated fats.

By running the chunk below, load the data.

```{r}
##KEEPIT##
foods_file <- "https://raw.githubusercontent.com/MichielNoback/intro_R_lessons/gh-pages/data/food_constituents.txt"
foods <- read.table(foods_file, header = TRUE)
head(foods)
```

## Analyse!

Solve the assignments by filling in your solutions where it says **`##YOUR CODE HERE`**
When you're done, Knit the document into Word and submit that with the rest of your test results.

**Question R-1 (2 points)**  

Show the data from columns one, five and six, rows 8-11.

```{r}
foods[8:11, c(1, 5, 6)]
```

**Question R-2 (2 points)**  

Show the Type, kcal and total fat for the food with the highest total fat content.

```{r}
foods[foods$fat.total == max(foods$fat.total), c(2, 3, 8)]
```

**Question R-3 (4 points)**  

Given the dataframes in the chunk below, study the documentation of the `merge()` function. Next, merge the two dataframes without any data loss.

```{r}
##KEEPIT##
students1 <- data.frame(
    name = c("Mark", "Emily", "John"),
    biology = c(4.5, 6.2, 8.1),
    chemistry = c(6.1, 7.2, 9.3)
) 
students2 <- data.frame(
    first_name = c("Emily", "John", "Peter"),
    statistics = c(3.8, 6.6, 6.8)
)
students1
students2
```

```{r}
merge(students1, students2, by.x = "name", by.y = "first_name", all = TRUE)
```


**Question R-4 (4 points)**  

Create a scatterplot showing the relationship between `kcal` and `carb.total`. Make sure you have correct axis labels. Think about which one you put on the x-axis!

```{r}
#We do not know the units so they are left out
plot(foods$carb.total, foods$kcal, xlab="Total Carbohydrate", ylab = "Calories (kcal)")
```

